OpenMPIR

### 2017-10-05 paper.tex
Another small tweak.

While there is general agreement that there needs to be IR support for
parallelism in parallel programs, there isn't consensus on which of these
approaches is best. Approaches that are easier at first, such as metadata
or intrinsic approaches, are similarly easy to extend to become unwieldy. There is
a reason that it's difficult to add instructions to LLVM: any added IR
construct needs to be considered in many locations. From debugging by printing
out IR, to case analysis for different control flow constructs, having 
a proper set of instructions to denote parallelism has numerous advantages. 
Additionally, any hope of having a formal semantics for an IR depends on a 
simple, concise set of parallelism constructs, something that metadata and
intrinsics approaches can easily avoid.

A related approach to composing programming models is to keep the same code
generation approach, but replace calls into built in runtimes with calls into a
shared runtime. This is the approach taken by Lithe, where Pan et
al.\ compose programs using both GNU OpenMP and Intel TBB~\cite{lithe}. This approach succeeds
in composing different programming models at run-time, but doesn't enable the
static analyses that are enabled by Tapir.

>>>>

While there is general agreement that there needs to be IR support for
parallelism in parallel programs, there isn't consensus on which of these
approaches is best. Approaches that are easier at first, such as metadata
or intrinsic approaches, are similarly easy to extend but can become unwieldy. There is
a reason that it's difficult to add instructions to LLVM: any added IR
construct needs to be considered in many locations. From debugging by printing
out IR, to case analysis for different control flow constructs, having 
a proper set of instructions to denote parallelism has numerous advantages. 
Additionally, any hope of having a formal semantics for an IR depends on a 
simple, concise set of parallelism constructs, something that metadata and
intrinsics approaches can easily avoid.

A related approach to composing programming models is to keep the same code
generation approach, but replace calls into built-in runtimes with calls into a
shared runtime. This is the approach taken by Lithe, where Pan et
al.\ compose programs using both GNU OpenMP and Intel TBB~\cite{lithe}. This approach succeeds
in composing different programming models at run-time, but doesn't enable the
static analyses that are enabled by Tapir.
